---
output: pdf_document
---
#Practical Machine Learning Assignment: Writeup

##1. Synopsis
The goal of this project is to predict the manner in which people did the exercise, includes:

- Create a report describing how to built the model;
- how to use cross validation;
- what I think the expected out of sample error is;
- why I made these choices;
- Finally use the prediction model to predict 20 different test cases.

##2. Load the Caret Library and Set the Random Number Generator's Seed
The purpose of setting the random number generator's seed is to ensure reproducibility.

```{r echo=TRUE, results='hide'}
library(caret)
set.seed(1234)
```

##3. Pre-Processing of Data

```{r echo=TRUE, results='hide'}
rawData <- read.csv("pml-training.csv", na.strings=c("NA",""), strip.white=T)
Totalna <- apply(rawData, 2, function(x) { sum(is.na(x)) })
cleandata <- subset(rawData[, which(Totalna == 0)], select=c(roll_belt, pitch_forearm, yaw_belt, magnet_dumbbell_y, pitch_belt, magnet_dumbbell_z, roll_forearm, accel_dumbbell_y, roll_dumbbell, magnet_dumbbell_x,classe))
```

##4. Partition
Set the training/testing partition using the training data set.

```{r echo=TRUE}
inTrain <- createDataPartition(cleandata$classe, p=0.7, list=F)
training <- cleandata[inTrain,]
testing <- cleandata[-inTrain,]
```

##5. Learning the Clasification Hypothesis using the Training Data

###5.1 Training a Random Forest model.

```{r echo=TRUE}
#Fitting the Model
ctrl <- trainControl(allowParallel=T, method="cv", number=4)
modFit<-train(classe~.,data=training,method="rf",trControl=ctrl)
#Visualizing the Model Results
modFit
```

###5.2 Confusion matrix.

```{r echo=TRUE}
predictions<-predict(modFit,newdata=testing)
confusionMatrix(predictions,testing$classe)
```
Its accuracy on the test set is 98.4%

##6. Predictions

```{r echo=TRUE}
rawdata2 <- read.csv("pml-testing.csv", na.strings=c("NA",""), strip.white=T) 
predictions2 <- predict(modFit, newdata=rawdata2)
predictions2
```
